### 2023-02-12 README.Rmd
Add warning in README [no ci]
Rename gran in README and logo
ref #35

# gran <img src="man/figures/gran_logo.svg" align="right" height="200" />

<!-- badges: start -->
[![R-CMD-check](https://github.com/chainsawriot/gran/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/chainsawriot/gran/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of gran (gran: R anachronism nullifier) [^gesis] is to obtain the dependency graph of R packages at a specific time point.

Although this package can also be used to ensure the current R computational environment can be reconstructed by future researchers, this package gears towards reconstructing historical R computational environments which have not been completely declared. For the former purpose, packages such as [renv](https://github.com/rstudio/renv/), [groundhog](https://github.com/CredibilityLab/groundhog), [miniCRAN](https://github.com/andrie/miniCRAN), and [Require](https://github.com/PredictiveEcology/Require) should be used. One can think of gran as an archaeological tool.

@@

@@

You can install the development version of gran like so:

``` r
remotes::install_github("chainsawriot/gran")
```

@@

```r
library(gran)
graph <- resolve(pkgs = c("openNLP", "LDAvis", "topicmodels", "quanteda"),
                 snapshot_date = "2020-01-16")
```

@@

The resolved result is an S3 object called `granlist` and can be exported as an installation script. The installation script can be execute on a vanilla R installation.

```r
export_granlist(graph, "gran.R")
```

@@

A `granlist` object can be used to recreate the computational environment via [Rocker](https://github.com/rocker-org/rocker). Please note that the oldest R version one can get from Rocker is R 3.1.0.

@@

```bash
cd ~/rocker_test
sudo docker build -t gran .
sudo docker run --rm --name "grantest" -ti gran
```

@@

```bash
cd ~/rocker_test
sudo docker build -t gran .
sudo docker run -p 8787:8787 -e PASSWORD=abc123 --rm --name "grantest" -ti gran
```

@@

`gran` can still be used to recreate computational environments for R < 3.1.0. The Dockerfile generated is based on Debian Woody (3.0) and the requested version of R is compiled from source. As of writing, this method works for R < 3.1.0 but not R < 2.1.0. The `image` parameter is ignored in this case.

```r
gran_rio <- resolve("rio", snapshot_date = "2013-08-28") ## R 3.0.1
dockerize(gran_rio, output_dir = "~/old_renviron")
```

@@

The logo of gran is a remix of [this](https://commons.wikimedia.org/wiki/File:Flag_of_the_Canary_Islands.svg) public domain image. The two dogs should be *Presa Canario*, the native dog breed on the islands of Gran Canaria and Tenerife.

@@

[^gesis]: Actually, it stands for "GESIS R Archive Network".

>>>>

# rang <img src="man/figures/rang_logo.svg" align="right" height="200" />

<!-- badges: start -->
[![R-CMD-check](https://github.com/chainsawriot/rang/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/chainsawriot/rang/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of rang (Reconstructing Ancient Number-crunching Gears) [^gesis] is to obtain the dependency graph of R packages at a specific time point.

Although this package can also be used to ensure the current R computational environment can be reconstructed by future researchers, this package gears towards reconstructing historical R computational environments which have not been completely declared. For the former purpose, packages such as [renv](https://github.com/rstudio/renv/), [groundhog](https://github.com/CredibilityLab/groundhog), [miniCRAN](https://github.com/andrie/miniCRAN), and [Require](https://github.com/PredictiveEcology/Require) should be used. One can think of rang as an archaeological tool.

@@

**Important:** This package is in a very early stage. API might still change.

@@

You can install the development version of rang like so:

``` r
remotes::install_github("chainsawriot/rang")
```

@@

```r
library(rang)
graph <- resolve(pkgs = c("openNLP", "LDAvis", "topicmodels", "quanteda"),
                 snapshot_date = "2020-01-16")
```

@@

The resolved result is an S3 object called `rang` and can be exported as an installation script. The installation script can be execute on a vanilla R installation.

```r
export_rang(graph, "rang.R")
```

@@

A `rang` object can be used to recreate the computational environment via [Rocker](https://github.com/rocker-org/rocker). Please note that the oldest R version one can get from Rocker is R 3.1.0.

@@

```bash
cd ~/rocker_test
sudo docker build -t rang .
sudo docker run --rm --name "rangtest" -ti rang
```

@@

```bash
cd ~/rocker_test
sudo docker build -t rang .
sudo docker run -p 8787:8787 -e PASSWORD=abc123 --rm --name "rangtest" -ti rang
```

@@

`rang` can still be used to recreate computational environments for R < 3.1.0. The Dockerfile generated is based on Debian Woody (3.0) and the requested version of R is compiled from source. As of writing, this method works for R < 3.1.0 but not R < 2.1.0. The `image` parameter is ignored in this case.

```r
rang_rio <- resolve("rio", snapshot_date = "2013-08-28") ## R 3.0.1
dockerize(rang_rio, output_dir = "~/old_renviron")
```

@@

The logo of rang is a remix of [this](https://commons.wikimedia.org/wiki/File:Flag_of_the_Canary_Islands.svg) public domain image. The two dogs should be *Presa Canario*, the native dog breed on the islands of Gran Canaria and Tenerife.

@@

[^gesis]: It stands for "R Archiving Nerds at GESIS". The package was previously named `gran`, but we decided to rename it to `rang` because there is another package named [gRAN](https://cran.r-project.org/web/packages/GRANBase/vignettes/GRAN_Overview.html).
